Model validation plots

### 2021-05-24 doc/validate_models.Rmd
addresses #56

```{r load-targets}
withr::with_dir(here::here(),{
  tar_load(c(s_cf, s_1ha, g_cf, g_1ha, f_cf, f_1ha))
  })
```

@@

@@

@@

```{r}
gratia::appraise(g_cf)
```

@@

@@

@@

```{r}
par(mfrow = c(2,2))
#histogram
plot(density(qresid(f_1ha)))
#QQ plot
qqnorm(qresid(f_1ha)); qqline(qresid(f_1ha))
#Fitted vs. residuals
scatter.smooth(predict(f_1ha, type = "response"), qresid(f_1ha), col = "grey")
```

>>>>

```{r load-targets}
withr::with_dir(here::here(),{
  tar_load(c(
    s_cf,
    s_1ha,
    g_cf,
    g_1ha,
    f_cf,
    f_1ha,
    s_cf_sub,
    g_cf_sub,
    f_cf_sub
    ))
  })
```

@@

Quantile residuals are more appropriate for binomial models.
### Fragments

@@

### Continuous forest subsample

To check that differences are not purely due to sample size differences, particularly that lower edf in continuous forests is due to higher sample size.  For survival, edf is actually higher in CF with a larger sample size.  With subsample, edf are more similar.

```{r}
summary(s_1ha)$edf[3]
summary(s_cf)$edf[3]
summary(s_cf_sub)$edf[3]
```

```{r}
draw(s_cf_sub)
```
Surface still looks different in a similar way though.

@@

@@

```{r}
gratia::appraise(g_cf)
```
### Continuous Forest subsample

To check that differences are not purely due to sample size differences, particularly that lower edf in continuous forests is due to higher sample size.

```{r}
summary(g_1ha)$edf[3]
summary(g_cf)$edf[3]
summary(g_cf_sub)$edf[3]
```
edf of subsample is similar to full dataset, despite differences in sample size.

```{r}
draw(g_cf_sub)
```
Crossbasis surface looks nearly identical.

@@

```{r}
par(mfrow = c(2,2))
#histogram
plot(density(qresid(f_1ha)))
#QQ plot
qqnorm(qresid(f_1ha)); qqline(qresid(f_1ha))
#Fitted vs. residuals
scatter.smooth(predict(f_1ha, type = "response"), qresid(f_1ha), col = "grey")
```
### Continuous Forest

@@

### Continuous Forest subsample
To check that differences are not purely due to sample size differences, particularly that lower edf in continuous forests is due to higher sample size.  For flowering, edf is actually slightly higher in CF with a larger sample size.  With subsample, edf are more similar.

```{r}
summary(f_1ha)$edf[3]
summary(f_cf)$edf[3]
summary(f_cf_sub)$edf[3]
```

```{r}
draw(f_cf_sub)
```
Crossbasis surface looks extremely similar.
